On the presentation of orthogonal groups over polynomial rings

### 2019-05-22 dl-paper.tex
Fixed some issues

\begin{corollary} \label{Kgen-strong}
 For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\St(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(f, \eta)$, $f \in M[X]$, $\eta \in XA[X]$.
\end{corollary}
\begin{proof}
 Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
 Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to 
 $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
 Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$
 belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$.
 Similar argument also works for the negative roots, and the required assertion now follows.
\end{proof}

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
\begin{enumerate}
 \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, \xi),\ \beta \in Z_0(\alpha);$
 \item $x_{-\alpha}(X^2f);$
 \item $x_{\alpha}(f)$.
\end{enumerate}
In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. \end{df}

\begin{rem}\label{rem:c-DS}
From our assumptions on $\Phi$ it follows that $Z_0(\alpha)$ is nonempty, hence $P_\alpha(0)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ ($a\in A$, $m\in M$) and elements $c_{\pm \gamma}(f, X\xi)$ for $\gamma \in Z_0(\alpha)$ (both can be expressed as products of generators of type 3).
\end{rem}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(Xm)$, $m \in M$. The following lemma shows that the resulting subgroup is sufficiently large.
\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$. The required assertion now follows from~\cref{Kgen-strong} and the preceding remark. \end{proof}

\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists of images under $j_+$ of those elements 
 $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M) := \Img(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)) \ltimes \hat{U}(Z_+(\alpha), M)$ 
 (i.\,e. the subgroup generated by elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
 and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}). \end{rem}

@@

Suppose $g$ has type 1 or 2 and $\beta - \alpha \in \Phi$. By~\cref{Zrels} we obtain that
\begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \nonumber \end{align}
The expressions in the right hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.

Suppose $g$ has type 1 and  $\alpha + \beta \in \Phi$. By~\cref{Zrels} 
\begin{equation} \label{eq3-2} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
and the latter expression is a product of generators of type $4, 1, 1$.

@@

\begin{lemma} \label{lem:Tulenbayev-formula} 
One has 
$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein} shows that
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
\end{multline*}
which implies the assertion.
\end{proof}

@@

 The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
 $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position conjugating by $x_{\epsilon}(mX)$ all factors along the way.
 Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after simplification of these conjugates, so this process is guaranteed to terminate.
 To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
 (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them) have terms of degree at least $2$ in $X$.

@@

\subsection{The proof of the injectivity theorem}
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.

\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \] 
Denote by $\overline{G}_M^0$ the image of the left arrow $i_-$ in $G^{\leq 0}$.

Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times G^{\leq 0} \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
$p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
We let $\overline{G}_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot h_0, u)$, $h_0 \in \overline{G}_M^0$.
It is clear that this action is well defined. Denote by $\overline{V}$ the quotient set $V / \overline{G}_M^0$.

@@

\begin{lemma} Let $\Phi$ be any root system of rank $\geq 3$, $\alpha \in \Phi$ and $(A, M)$ be a local pair.
 Then the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $c = [g, h, u] \in \overline{V}$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $(g, h \cdot i_+(h_0), u)$ is the representative of $c$ on which $t_\alpha(aX^{-1})$ is defined.

 Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
 Let $(g, h_1, u), (g, h_2, u)$ be a pair of representatives of the same $c \in \overline{V}$ for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ lie in $P_\alpha(*)$.
 By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in \overline{\St}(\Phi, A, M)$, moreover, 
  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
 By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
 From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
 the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, therefore $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
 By~\cite[Theorem~2.5]{Ste73} the latter subgroup is generated by relative Steinberg symbols $\{ a, m \}_\beta$, where $\beta$ is any fixed long root of $\Phi$.
 It is not hard to check using e.\,g. the table on p.~986 of~\cite{St71} that $Z_0(\alpha)$ always contains a long root, therefore
  $\overline{\K_2}(\Phi, A, M)$ is contained in $Z_\alpha(A, M)$ by ??? hence $h_0 \in Z_\alpha(A, M)$.
 Thus, we have shown that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$ therefore
 \begin{multline} \nonumber
  T_\alpha(aX^{-1})[g, h_1, u] = \left[ x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right] = \\
  = \left[ x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right] = T_\alpha(aX^{-1})[g, h_2, u]. \qedhere
 \end{multline} \end{proof}

>>>>

\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by
 $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
 Invoking~\eqref{C4} of~\cref{Crels} with $\xi = 1$, $s = m$, $t = X\eta$ we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to 
 $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
 Arguing by induction on the height of $\alpha$ we conclude that $c_\alpha(m, X\eta)$ for all $\alpha \in \Phi^+$
 belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(m, X\eta)$.
 Similar argument also works for the negative roots, and the required assertion now follows. \end{proof}

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} 
Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.

Consider the following root subsets of $\Phi$ (cf.~\cite[Proposition~5.7]{St71}):
\begin{equation} \nonumber \begin{align}
   Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
   Z_0(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle = 0 \}, \\
   Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} \end{equation}

We denote by $Z_\alpha(A, M)$ the subgroup of $\overline{\St}(\Phi, A, M)$ generated by elements
 $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$.
It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes \hat{U}(Z_+(\alpha), M). \]
Notice that the subgroup $Z_\alpha(A, A)$ coincides with $Z(\hat{U}_\alpha)$ defined in~\cite[984]{St71}.

\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, 
hence $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^*$, $m\in M$. \end{rem}

\begin{df} \label{defP0} Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
\begin{enumerate} \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, \xi),\ \beta \perp \alpha;$
 \item $x_{-\alpha}(X^2f);$
 \item $x_{\alpha}(f)$. \end{enumerate}
In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. \end{df}

\begin{rem}\label{rem:c-DS} It is easy to check that $P_\alpha(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
In particular, it contains the relative Dennis--Stein and Steinberg symbols.
It is also clear that $P_\alpha(0)$ contains the elements $c_{\pm \beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
 (they can be factored as products of two elements of type 2 or 3). \end{rem}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
The following lemma shows that the resulting subgroup is sufficiently large.
\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$. The required assertion now follows from~\cref{Kgen-strong} and the preceding remark. \end{proof}

\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists precisely of images under $j_+$ of all elements 
 $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}

@@

Suppose $g$ has type 1 or 2 and $\beta - \alpha \in \Phi$. By~\cref{Zrels} we obtain that
\begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \label{eq3-2} \end{align}
The expressions in the right hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.

Suppose $g$ has type 1 and  $\alpha + \beta \in \Phi$. By~\cref{Zrels} 
\begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
and the latter expression is a product of generators of type $4, 1, 1$.

@@

\begin{lemma} \label{lem:Tulenbayev-formula} 
One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein} shows that
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}, \end{multline*}
which implies the assertion. \end{proof}

@@

 The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
 $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position conjugating by $x_{\epsilon}(mX)$ all factors along the way.
 Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after simplification of these conjugates, so this process is guaranteed to terminate.
 To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-3} 
 (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them) have terms of degree at least $2$ in $X$.

@@

\subsection{The proof of the injectivity theorem}
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
For shortness we also write $G_M^0$ instead of $\overline{\St}(\Phi, A, M)$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
$p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
It is clear that this action is well defined.
Denote by $\overline{V}$ the set of orbits of the action of $G_M^0$ on $V$.
Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$.

@@

\begin{lemma} Let $\Phi$ be any root system of rank $\geq 3$, $\alpha \in \Phi$ and $(A, M)$ be a local pair.
 Then the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, while the latter triple also lies in the same orbit as $(g, h, u)$.

 Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
 Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
 By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
 By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
 From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
 the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
 By~\cite[Theorem~2.5]{Ste73} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}_\beta$, where $\beta$ is any fixed long root of $\Phi$,
 It is not hard to check using e.\,g. the table on p.~986 of~\cite{St71} that $Z_0(\alpha)$ always contains a long root, therefore
  $\overline{\K_2}(\Phi, A, M)$ is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS} hence $h_0 \in Z_\alpha(A, M)$.
 Thus, we have shown that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
 \begin{multline} \nonumber
  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
 \end{multline} \end{proof}
